Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2017-05-26 cbm-rbd-paper.tex
SDFs comments part 3

We now explain in more detail the case study used for the previous illustrative figures.
We use the simplified automotive brake system as introduced in Section~\ref{sec:sysrel},
see Figure~\ref{fig:brakesys-layout} for the reliability block diagram.

@@

The effect of the continuous parameter update in our policy is illustrated in Figure~\ref{fig:tauhist1fig3T}.
There, the results as seen already in Figure~\ref{fig:tauhist1fig2T} are compared
to the case when component parameters are not updated during the operation of the system,
while still accounting for the fact that components age,
and that a failed component changes the system layout.
%***so dynamic but not adaptive?***
We see that $\tausnow$ (left panel) is decreasing more quickly in the no update case,
with the jumps at component failure times being less pronounced than in the update case.
Without the continuous update, residual system lifetime continues to be underestimated,
and maintenance is scheduled too early,
%$\tausnow$ (left panel) is consistently lower for the non-adaptive algorithm,
%same with $\tstarnow$ (center panel).
%This is because the adaptive algorithm recognizes that system components are more reliable than expected,
leading to lower expected operational cycle cost rates $\gstarnow$ (right panel).
$\tausnow$ for the policy without parameter update drops below $\delta = 0.1$ at $\tnow = 4$,
while maintenance is triggered for the algorithm with parameter update at $\tnow = 6$.
The parameter update thus allows to run the system for two more time units,
corresponding to a unit cost rate of $0.2 / 6 = 0.033$ instead of $0.2 / 4 = 0.05$,
a reduction of 33\%.

@@

Here, both corrective and age-based policies cannot avoid system failures entirely.
The condition-based policies result in two to three system failures in the $20 \times 5 = 100$ system runs,
whereas the age-based policies result in nine to ten system failures.
System runtimes are less variable for the age-based policies
since they do not use the current system structure information, %available information on the component level,
i.e., which components have failed and which not. %during operational cycles
System runtimes are more variable for the condition-based policies,
but longer on average, leading to lower realized cost rates.
Again, CBM-cpu performs slightly better than CBM-epu
as it has the possibility to learn within an operational cycle as well.
CBM-npu does surprisingly well, considering that it never updates prior component parameters. 
This confirms the observation from Section~\ref{sec:ex-3}
that current system structure information delivers a major part of the gains for our CBM policy.

@@

***Another way to relax the assumption of precise component monitoring
is to consider unreliable detection of component failures.
Our approach may be quite sensitive to the non-detection of component failures,
and one could tackle this by including a probabilistic observation model,
which assigns probabilities to false positives and false negatives in the component monitoring.***

***We also assume that the component-specific Weibull shape parameters are known,
and update only the scale parameters.
We restricted ourselves to this simplistic modelling
to allow for a clear and straight-forward demonstration of the general approach.
In a practical application, the shape parameters should be jointly updated together with the scale parameters.
This could be implemented by adopting the discretized approach by \cite{1969:soland}.***

@@

***A further simplifying assumption relates to the cost of preventive and corrective replacements,
which we consider as fixed.
In many real-life applications, maintenance costs vary over time
(e.g., increased labour cost due to overtime or night shift premiums),
and may depend on the number of failed components, or even on the exact system state.
In our approach, time-dependent cost structures can be easily accounted for,
by letting $c_p$ and $c_c$ in \eqref{eq:gtau} depend on $\tau$.
It will be more complex to account for costs that are dependent on the system state,
but our approach already provides the necessary information
in form of the posterior predictive distributions derived in Section~\ref{sec:postpred}.***
%since the calculation of $\Rsysnow(t)$ involves

Another promising extension would be to use sets of conjugate priors for the component models.
This approach is described in \cite{2016:walter-coolen},
leading to sets of current residual life distributions $\Rsys(t)$.
Consequently, we would obtain a set of expected operational cycle cost rate functions $\gnow(\tau)$.
The determination of the (set of) optimal time(s) to maintenance $\tausnow$
is then non-trivial,
and would involve decision criteria discussed in the imprecise probability literature,
like E-admissibility, maximality, or maximin \citep[see, e.g., \S 8][]{itip}.

>>>>

We now explain in more detail the case study used for the previous illustrative figures
(Figures~\ref{fig:ghist1fig2T} and \ref{fig:tauhist1fig2T}).
We use the simplified automotive brake system as introduced in Section~\ref{sec:sysrel},
see Figure~\ref{fig:brakesys-layout} for the reliability block diagram.

@@

The effect of the continuous parameter update in our policy is illustrated in Figure~\ref{fig:tauhist1fig3T}.
There, the results as seen already in Figure~\ref{fig:tauhist1fig2T} are compared
to the case when component parameters are not updated during the operation of the system,
while still accounting for the fact that components age,
and that a failed component changes the system layout.
%***so dynamic but not adaptive?***
We see that $\tausnow$ (left panel) is decreasing more quickly in the no update case,
with the jumps at component failure times being less pronounced than in the update case.
Without the continuous update, residual system lifetime continues to be underestimated,
and maintenance is scheduled too early,
%$\tausnow$ (left panel) is consistently lower for the non-adaptive algorithm,
%same with $\tstarnow$ (center panel).
%This is because the adaptive algorithm recognizes that system components are more reliable than expected,
leading to higher expected operational cycle cost rates $\gstarnow$ (right panel).
$\tausnow$ for the policy without parameter update drops below $\delta = 0.1$ at $\tnow = 4$,
while maintenance is triggered for the algorithm with parameter update at $\tnow = 6$.
The parameter update thus allows to run the system for two more time units,
corresponding to a unit cost rate of $0.2 / 6 = 0.033$ instead of $0.2 / 4 = 0.05$,
a reduction of 33\%.

@@

Here, most condition-based and all age-based policies cannot avoid system failures entirely.
Both CBM-epu and CBM-npu result in one system failure in the $20 \times 5 = 100$ system runs,
whereas the two age-based policies each result in ten system failures.
System runtimes are less variable for the age-based policies
since they do not use the current system structure information, %available information on the component level,
i.e., which components have failed and which not. %during operational cycles
System runtimes are more variable for the condition-based policies,
but longer on average, leading to lower realized cost rates.
Again, CBM-cpu performs slightly better than CBM-epu
as it has the possibility to learn within an operational cycle as well,
managing to avoid system failures entirely. 
Still, CBM-npu does surprisingly well, considering that it never updates prior component parameters. 
This confirms the observation from Section~\ref{sec:ex-3}
that current system structure information delivers a major part of the gains for our CBM policy.

@@

Another way to relax the assumption of precise component monitoring
is to consider unreliable detection of component failures.
Our approach may be quite sensitive to the non-detection of component failures,
and one could tackle this by including a probabilistic observation model,
which assigns probabilities to false positives and false negatives in the component monitoring.

We also assume that the component-specific Weibull shape parameters are known,
and update only the scale parameters.
We restricted ourselves to this simplistic modelling
to allow for a clear and straight-forward demonstration of the general approach.
In a practical application, the shape parameters should be jointly updated together with the scale parameters.
This could be implemented by adopting the discretized approach by \cite{1969:soland}.

@@

A further simplifying assumption relates to the cost of preventive and corrective replacements,
which we consider as fixed.
In many real-life applications, maintenance costs vary over time
(e.g., increased labour cost due to overtime or night shift premiums),
and may depend on the number of failed components, or even on the exact system state.
In our approach, time-dependent cost structures can be easily accounted for,
by letting $c_p$ and $c_c$ in \eqref{eq:gtau} depend on $\tau$.
It will be more complex to account for costs that are dependent on the system state,
but our approach already provides the necessary information
in form of the posterior predictive distributions derived in Section~\ref{sec:postpred}.
%since the calculation of $\Rsysnow(t)$ involves

Another promising extension would be to use sets of conjugate priors for the component models.
This approach is described in \cite{2016:walter-coolen},
resulting in sets of residual life distributions $\Rsysnow(t)$,
%Consequently, we would obtain a set of expected operational cycle cost rate functions $\gnow(\tau)$.
and this would lead to sets of expected operational cycle cost rate functions $\gnow(\tau)$.
The determination of the (set of) optimal time(s) to maintenance $\tausnow$
is then non-trivial,
and would involve decision criteria discussed in the imprecise probability literature,
like E-admissibility, maximality, or maximin \citep[see, e.g., \S 8][]{itip}.
